Viscous Transport in Eroding Porous Media

### 2019-05-31 docs/transport/erosion_transport.tex
do the result section in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. Let the initial radius of the body be $r$, the initial length of the body be $L$, 
and $d$ be the minimum initial distance from body to wall. Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer boundary and discretization points on the bodies, respectively.  We fix $N_\out=1024$ for all the simultions. We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}. We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in the shear flow. 
This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
The velocity of flow from the left side of $\Omega$ is 
$$\vv=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
We place a single eroding body close to the no-slip wall ($y=-1$).
This example has no pressure drop. 
We investigate the shape of eroding body when it is close to a solid wall at the three  
distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .

@@

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed pressure drop condition. The color is the vorticity of the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 has almost completely eroded.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, 
we are able to capture the details in the fluid when wall 
and bodies or body and bodies are close to each other. 
The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
The initial velocity of flow from the left side of $\Omega$ is 
$$\vv=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$ 
where $U$ is chosen such that 
the pressure drop between  $x=-2$ and $x=2$ remains fixed at 8.
With this choice, the velocity in the absent of grains has flow rate $U=1$.
The number of discretization points is $N_\iin = 256$.

@@

Since we use a Barycentric quadrature rule to approximate the velocity of tracers
and apply the fourth order Runge Kutta method to find the new locations of tracers in each step,
the tracers can be very close to but not penetrate the bodies. 
Those body-closed tracers are moving perfectly 
so we are able to observe the details of the interaction of bodies and fluid.
Although the direction of flow is from left to right, 
the tracers will not only travel horizontally but also vertically. 
In the last three frames of Fig.~\ref{fig:Eroding20tracer}, 
some tracers climb up from right to left around the body. 
There are zoom windows of the climbing tracers trajectories 
in Fig.~\ref{fig:Eroding20zoom} and they are taken from the 
last three frames of Fig.~\ref{fig:Eroding20tracer} with more tracers. 
In Fig.~\ref{fig:Eroding20zoom} the tracers around 
the center body first go from the channel below the body, 
climb up to the left, then go to the right and join another tracers 
in the channel above the body. 
 }

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. Let the initial radius of the body be $r$, the initial length of the body be $L$, 
and $d$ be the minimum initial distance from body to wall. Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer boundary and discretization points on the bodies, respectively.  We fix $N_\out=1024$ for all the simultions. We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}. We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in the shear flow. 
This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
The initial velocity of flow from the left side of $\Omega$ is 
$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
We place a single eroding body close to the no-slip wall ($y=-1$).
This example has no pressure drop. 
We investigate the shape of eroding body when it is close to a solid wall at the three  
distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .

@@

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed pressure drop condition. The color is the vorticity of the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 has almost completely eroded.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, 
we are able to capture the details in the fluid when wall 
and bodies or body and bodies are close to each other. 
The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
The initial velocity of flow from the left side of $\Omega$ is 
$$\UU(\xx)=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$ 
where $U$ is chosen such that 
the pressure drop between  $x=-2$ and $x=2$ remains fixed at 8.
With this choice, the velocity in the absent of grains has flow rate $U=1$.
The number of discretization points is $N_\iin = 256$.

@@

Since we use a Barycentric quadrature rule to approximate the velocity of tracers
and apply the fourth order Runge Kutta method to find the new locations of tracers in each step,
the tracers can be very close to but not penetrate the bodies. 
Those body-closed tracers are moving perfectly 
so we are able to observe the details of the interaction of bodies and fluid.
Although the direction of flow is from left to right, 
the tracers will not only travel horizontally but also vertically. 
In the last three frames of Fig.~\ref{fig:Eroding20tracer}, 
some tracers climb up from right to left around the body. 
There are zoom windows of the climbing tracers trajectories 
in Fig.~\ref{fig:Eroding20zoom} and they are taken from the 
last three frames of Fig.~\ref{fig:Eroding20tracer} with more tracers. 
In Fig.~\ref{fig:Eroding20zoom} the tracers around 
the center body first go from the channel below the body, 
climb up to the left, then go to the right and join another tracers 
in the channel above the body.

In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding. At the beggining, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing

The flow rate increases exponentially with growth rate close to $\ln10^4$. 
 }

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly touching eroding bodies and the eroding speed verse time.}
\end{figure}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
\end{figure}
